---
title: "GT Package"
output:
   html_document:
    toc: true
    toc_float: true
    number_sections: true
    toc_depth: 3
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r  cache=FALSE}
library(tidyverse)
library(gt)

martians <- read_tsv("../data/martians.txt")
```

# Demo 

```{r}
martians
```
## Inserting the Martians data set using gt package:
I have added a date column for one of the next exercises.
```{r}
martians %>% 
  gt()

```
## Grouping 
Here we have grouped the data by the sites
```{r}
tab <- martians %>% 
  gt(
    groupname_col = "Site",
    rowname_col = "Nose"
  )
tab
```

## Formating the Variables 

Here we have changed the speed decimals having some scientific notation looks 
```{r}
tab_2 <- tab %>% 
  fmt_scientific(
    columns = c(Speed.Mars, Speed.Earth),
    decimals = 1
  )
tab_2
```

## Hiding Columns 

Hiding the columns would not affect any computations on the hidden columns, they are still usable. 

```{r}
tab_3 <- tab_2 %>% 
  cols_hide(
    columns = c(EyeIndex, Eye, Ratio, Age, Aptitude, BMI, Group, AgeIndex, Height_UnequalVar, Height_UnequalVar8)
  )
tab_3
```
## Footnote 
### Footnote on a cell

```{r}
tab_4 <- 
  tab_3 %>% 
  tab_footnote(
    footnote = "These are shortest martians.",
    locations = cells_body(
      columns = Height,
      rows = Height < 200
    )
  )
tab_4
# # info_date_style()
# info_paletteer()
```


```{r}
tab_5 <- 
  tab_4 %>% 
  tab_footnote(
    footnote = "All values are in m/s",
    locations = cells_column_labels(
      columns = c(Speed.Mars, Speed.Earth)
    )
  )
tab_5
```
You don't need to worry about the order. GT package keep the order according to the first footnote execution.

```{r}

tab_6<-
  tab_5 %>% 
  tab_options(
    footnotes.marks  = "letters"
  )
tab_6
```

## Sources Note:
```{r}
tab_7<- 
tab_6 %>% tab_source_note(
  source_note = "Source: data folder in https://github.com/Scavetta/Misk-DSI-2021-01" 
)
tab_7
```


## Renameing/ Adding a Header 

adding a header and a subtitle to the table.
Also, when you want to use **bold** or *italic* use function `md()`.

```{r}
tab_8 <-
  tab_7 %>% 
  cols_label(
    Speed.Earth = "Speed in Earth",
    Speed.Mars = "Speed in Mars"

  ) %>% 
  tab_header(
    title = "The Martians Example",
    subtitle = md("Uses the *martians* data set provided by the **doctor**")
  )
tab_8
```



## Column Width 

```{r}

tab_9<-
  tab_8 %>%
  cols_width(everything() ~ px(100))
 tab_9
```
## Colors 

```{r}

  tab_9 %>% 
  data_color(
    columns = Antennae,
    colors = c("blue", "red")
  )
```
```{r}

  tab_9 %>% 
  tab_options(
    stub.background.color = "blue"
  )
```

```{r}
# # tab_10<-
#   tab_9 %>%
#   data_color(
#     columns = vars(Height),
#     colors = scales::col_numeric(
#       palette = c("white", "#104e8b"),
#       domian = NULL    )
#   )
```

